Optimal Light Curve Attitude Inversion with Measurement Noise: Two Case Studies

### 2025-03-18 paper.tex
corrected 3/18 comments

Understanding the orientation and angular velocity state of active or passive human-made space objects is critical for many space situational awareness operations like long-term orbit propagation, anomaly resolution, determining mission status, and active debris removal. Beyond low-Earth orbit, optical telescopes are predominantly used to track space objects. Due to atmospheric distortion and aperture size, it is generally impossible to resolve even large satellites and rocket bodies in optical ground-based imagery. As a result, shape and orientation information is unavailable in individual images, but a measurement of the object's total brightness can still be obtained. Even if the object's shape and reflective properties are known, any given brightness measurement will generally correspond to infinitely many possible orientations. To constrain the solution space, the brightness can be tracked over time -- producing a sequence of measurements called a light curve. If the object's identity is known, its attitude profile can be estimated from the light curve -- up to certain ambiguities -- through a process known as light curve attitude inversion. Due to the environmental and instrumental noise in the light curve, as well as symmetries in the observation geometry, there may be multiple attitude profiles that are equally likely to produce any given light curve. To identify these ambiguous solutions, global attitude inversion methods must thoroughly search the solution space.

In this work, we apply a BFGS-based global attitude inversion algorithm to real observations taken by the Purdue Optical Ground Station of a Delta I upper stage and the ECHOSTAR II satellite. Given a light curve with an estimate of the shape and reflective properties of the object, our procedure searches the space of initial orientations, angular velocities, and inertia tensors to find initial conditions that produce light curves with low error compared to the observed values. Our formulation inherently accounts for the multiple ambiguities resulting from the object and observation geometry, the physical constraints of torque-free rigid body motion, and noise in the light curve.

@@

Methods for estimating the attitude state of uncontrolled space objects from light curves differ significantly depending on the presence of an initial guess. If a guess is available, many filter-based approaches have been developed to process new photometry to update the guess orientation and angular velocity. This class of methods includes single Kalman filters \cite{burton2021two, gagnon2024, wetterer2009}, and multi-filter multiple-model adaptive estimation (MMAE) schemes \cite{linares2014space, dianetti2020}. These approaches can be very effective if the initial state estimate is close to the truth, but have been reported to diverge for orientation errors as small as $5^\circ$ in orientation and $0.03^\circ/s^{-1}$ in angular velocity \cite{gagnon2024} due measurement ambiguities and nonlinearity.

If no initial attitude state is available, as in most cases of passive debris observation, the inversion problem must be solved globally. Filtering approaches can be applied here too; particle \cite{linares2014particle, holzinger2014} and Bayesian Multi-Hypothesis filters \cite{burton2021two, cabrera2023} have shown promise in prior work. Bayesian methods may be ineffective if a reliable prior distribution for the attitude state is not available. In the absence of prior knowledge about the object's attitude state, simulated annealing \cite{gagnon2024, clark2020}, genetic algorithms \cite{gagnon2024, piergentili2017, clark2020}, and particle swarm optimizers (PSOs) \cite{clark2020, clark2022, burton2024journal, burton2024scitech, gagnon2024} can be applied to search the solution space exhaustively.

While much work has performed full state attitude inversion on simulated light curve data \cite{burton2024journal, gagnon2024, robinson2025att}, studies using real data often focus on determining a constant spin rate and axis of rotation for the observed object. Frequency analysis in the form of periodograms, Fourier transforms, or epoch folding, is often used to determine the spin rate based on the light curve's frequency spectrum \cite{silha2015, silha2021, isoletta2024, schildknecht2015, pittet2017, yanagisawa2012, koshkin2018}. If optical material properties are known, the width of a single specular glint can provide sufficient information to determine the rotation rate \cite{hinks2016}. There has also been interest in tracking the evolution of spin rates over time for different classes of objects in different orbital regimes \cite{koshkin2018, blacketer2022, karpov2016}. These spin rate determination methods are designed for single-axis rotations and can fail for tumbling objects.

@@

Works that seek to estimate a full rigid body attitude state from real data -- a time-varying orientation and angular velocity -- grid search \cite{shafer2017} and genetic algorithms \cite{piergentili2020, gallucci2020} have been used. These full-state estimation studies are limited by computational complexity, poor knowledge of material reflectivities, and the presence of measurement noise.

Our method is a global full-state attitude solver inspired by recent PSO work \cite{burton2024journal} but is easier to tune, can be fully parallelized, and is robust to significant measurement noise \cite{robinson2025att}. Further, our method differs from other global estimation methods in that we do not seek to find one optimal solution and instead search for a collection of high-quality local minima to directly study the many ambiguous solutions for a given light curve. Our approach was designed specifically for use with real data as we take time-varying measurement noise and uncertainties in the body moments of inertia into account explicitly.

@@

This work proceeds by describing the inversion method, discussing efficient methods for computing the time-varying probability density of the light curve. We present inversion results for a simulated rocket body light curve where the ground truth is known, followed by two cases -- a derelict satellite and rocket body -- using real light curve data collected by the Purdue Optical Ground Station. A deeper treatment of our method and additional simulated light curve results can be found in a forthcoming publication by the authors \cite{robinson2025att}.

@@

The state vector $\vctr{x}$ we optimize to fit the observed light curve is the concatenation of the Modified Rodriguez Parameter (MRP) $\vctr{p} = [p_1, p_2, p_3]^T$, the principal body frame angular velocity $\vctr{\omega} = [\omega_1, \omega_2, \omega_3]$ in radians per second, and the ratios of the principal moments of inertia $J_y / J_x$ and $J_z / J_x$ where the constant inertia tensor in principal axes is $J = \mathrm{diag}\left([J_x, J_y, J_z]\right)$:

@@

Our inversion method is based on the global minimization of a maximum-likelihood loss function which computes the negative log-likelihood of the observed light curve $\vctr{S}$ being a sample from the normal distribution defined by the estimated light curve mean $\hat{\vctr{S}}$ and the estimated standard deviation at each $k$th timestep $\sigma_k$:

@@

\subsection{Running the Solver} \label{sec:run_solver}

To initialize the solver, we initialize $n$ guesses scattered throughout the solution space -- possibly sampled from a prior distribution based on available knowledge. In the most basic case, the initial state guess is sampled for guess $i$ at iteration $k=0$:

@@

\noindent
In this work, $\vctr{p}_{i,0}(0)3$ is uniformly randomly sampled from orientation space, $\vctr{\omega}_{i,0}(0)$ is uniformly randomly sampled from the ball in $\mathbb{R}^3$ of radius $\norm{\vctr{\omega}}_\text{max}$ -- the maximum angular rate to search -- while $\left(J_y / J_x\right)_{i,0}$ and $\left(J_z / J_x\right)_{i,0}$ are sampled from Gaussian prior distributions centered at estimated values derived from the known geometry of the object. We determine $\norm{\vctr{\omega}}_\text{max}$ based on the maximum power positive frequency in the observed light curve $f^\star$ in Hertz and an arbitrary safety factor $f_\omega \geq 1$, selected as $f_\omega = 1.25$ for this work:

@@

@@

 In any particular illumination and observation condition, a fraction of the facet's area $\tilde{a}_i$ may be shadowed due to obstructing geometry before or after light reaches the surface element. The remainder of the facet's area $\bar{a}_i$ is unshadowed and contributes to the total flux reaching the observer from the object, such that the total area of each facet is $a_i = \tilde{a}_i + \bar{a}_i$. The geometry for an individual facet is displayed in Figure \ref{fig:facet_geom}.

@@

The unshadowed area $\bar{a}$ may be computed in several ways. For convex objects, $\bar{a}=a$ as self-shadowing is impossible. For highly nonconvex and detailed models composed of thousands of faces, $\bar{a}$ can be approximated on a pixel grid using shadow mapping \cite{robinson2022}. Self-shadowing can be efficiently solved semi-analytically for lower-fidelity approximations of real space object geometry by computing the mutual intersections of the polygons $P_k$ of other faces whose projections overlap with the face in question. Up to a maximum intersection depth $d$, the unshadowed area can be computed via:

@@

As the objects we investigate in this work are well-approximated with relatively simple non-convex meshes, we use the semi-analytic method to efficiently compute unshadowed areas via the Sutherland-Hodgeman algorithm \cite{sutherland1974} for each polygon intersection.

@@

This section summarizes an in-depth study of relevant noise sources in CCD and CMOS sensor light curves by the authors in a forthcoming publication \cite{robinson2025twin}.

@@

\begin{table}[H]
  \centering
  \caption{Reflection properties of materials used in the synthetic data test case. The authors estimated the white paint parameters qualitatively}
  \vspace*{6pt}
  \begin{tabular}{|l|l|l|l|}
  \hline
  \textbf{Material} & $C_d$ & $C_s$ & $n$ \\ \hline
 Aluminum \cite{fankhauser2023} & $0.34$ & $0.40$ & $8.9$ \\ \hline
 White paint & $0.9$ & $0.1$ & $1$ \\ \hline
  \end{tabular}
  \label{tb:synth_matprops}
\end{table}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\figmed]{light_curves_mag_rocket_body_sdc.png}
  \caption{Simulated observed V-band magnitude for the rocket body.}
  \label{fig:obs_mag_synth}
\end{figure}

@@

A total of $10^5$ initial state guesses are created via the sampling scheme described in Section \ref{sec:run_solver} with $\norm{\vctr{\omega}}_\text{max}=5.26$ degrees per second. The inertia tensor ratios are initialized by sampling a symmetric Gaussian distribution with $\sigma=0.05 \: [kg\cdot m^2]$ on each axis to simulate a moderate level of inertia uncertainty. BFGS minimization was then performed for each initial guess to locally solve the optimization problem given by Equation \ref{eq:opt_problem}. Classifying candidate solutions with $\ell = 1/10$ produces over $10^4$ solutions within this bound. Figure \ref{fig:conv_lcs_synth} shows the mean light curves produced by the identified candidate solutions. There is generally good agreement between the candidate light curves and the observations, indicating that high-quality local minima have been identified.

@@

Figures \ref{fig:sigma_sols1} and \ref{fig:omega_sols1} display the candidate MRP and angular velocity vectors of the best solutions determined via the procedure in Section \ref{sec:candidate_sols}. We notice that for both the initial orientation and angular velocity, the ground truth lies squarely in the surfaces of candidate solutions. In angular velocity space, most solutions fall onto the surface of two open-ended cylinders -- one with half the radius of the larger cylinder containing the truth. Similarly in orientation space, we solutions fall on two distinct manifolds -- likely resulting from a reflection of the object's body frame about the bisector between the Sun and observer vectors \cite{marto2024, burton2024journal}. One of these orientation-space surfaces contains the ground truth. These additional families of solutions highlight the reality that a wide variety of attitude profiles may produce the same observations.

@@

This light curve shows clear periodicity, but has a high estimated standard deviation and a relatively low sampling rate due to the object's low brightness and the sensor readout time. Inversion was performed using $10^4$ initial guesses with the material and angular velocity assumptions listed in Table \ref{tb:case2_ass}. The candidate solution results are presented in terms of their mean light curves in Figure \ref{fig:case2_s}, orientation MRPs and angular velocities in Figure \ref{fig:case2_pw}, and inertia ratios in Figure \ref{fig:case2_i}.

@@

Attitude information is critical for many tasks informing space situational awareness. Orientation and angular velocity data aids high-fidelity orbit propagation, mission recovery efforts, and object selection for active debris removal. Obtaining attitude information is often difficult, especially for passive debris objects. Due to atmospheric distortion and diffraction-limited optics, ground-based telescopes can only determine a total brightness received from a space object. If a shape model is known, the light curve -- a sequence of these brightness measurements -- is one tool for attitude estimation. We presented an approach for solving this highly nonlinear and non-convex optimization problem with a gradient-based multistart method. We presented attitude inversion results for one case with synthetic data and two cases with real observations. Unlike other approaches, our method successfully identifies the numerous ambiguous solutions families -- originating from symmetries in the observation geometry and the object shape -- which may produce the same observations. These disparate candidate solutions can serve as starting points for more detailed exploration as additional light curves or further object shape information is obtained.

>>>>

Understanding the orientation and angular velocity state of active or passive human-made space objects is critical for many space situational awareness operations like long-term orbit propagation, anomaly resolution, determining mission status, and active debris removal. Beyond low-Earth orbit, optical telescopes are predominantly used to track space objects. Due to atmospheric distortion and aperture size, it is generally impossible to resolve even large satellites and rocket bodies in optical ground-based imagery. As a result, shape and orientation information is unavailable in individual images, but a measurement of the object's total brightness can still be obtained. Even if the object's shape and reflective properties are known, any given brightness measurement will generally correspond to infinitely many possible orientations. To constrain the solution space, the brightness can be tracked over time -- producing a sequence of measurements called a light curve. If the object's identity is known, its attitude profile can be estimated from the light curve -- up to certain ambiguities -- through a process known as light curve attitude inversion. Due to symmetries in the observation geometry and object shape, there may be multiple attitude profiles that are equally likely to produce any given light curve. Environmental and instrumental measurement noise worsens these ambiguities. To reliably identify these ambiguous solutions, global attitude inversion methods must thoroughly search the solution space.

In this work, we apply a BFGS-based multi-start global attitude inversion algorithm to synthetic observations of an upper stage and real observations taken by the Purdue Optical Ground Station of a Delta I upper stage and the ECHOSTAR II satellite. Given a light curve with an estimate of the shape and reflective properties of the object, our procedure searches the space of initial orientations, angular velocities, and inertia tensors to find initial conditions that produce light curves with low error compared to the observed values. Our formulation inherently accounts for the aforementioned ambiguities, the physical constraints of torque-free rigid body motion, and the noise in the light curve.

@@

Methods for estimating the attitude state of uncontrolled space objects from light curves differ significantly depending on the presence of an initial guess. If a guess is available, many filter-based approaches have been developed to process new photometry to update the guess orientation and angular velocity. This class of methods includes single Kalman filters \cite{burton2021two, gagnon2024, wetterer2009}, and multi-filter multiple-model adaptive estimation (MMAE) schemes \cite{linares2014space, dianetti2020}. These approaches can be very effective if the initial state estimate is close to the truth, but have been reported to diverge even in cases when the initial guess guess is within $5^\circ$ of the ground truth orientation and $0.03^\circ/s^{-1}$ in angular velocity error \cite{gagnon2024} due to measurement nonlinearity and ambiguities.

If no initial attitude guess is available, as in most cases of passive debris observation, the inversion problem must be solved globally. Filtering approaches can be applied here too; particle \cite{linares2014particle, holzinger2014} and Bayesian Multi-Hypothesis filters \cite{burton2021two, cabrera2023} have shown promise in prior work, but still rely on high-quality priors as with the Kalman filters. In the absence of prior knowledge about the object's attitude state, simulated annealing \cite{gagnon2024, clark2020}, genetic algorithms \cite{gagnon2024, piergentili2017, clark2020}, and particle swarm optimizers (PSOs) \cite{clark2020, clark2022, burton2024journal, burton2024scitech, gagnon2024} can be applied to search the solution space exhaustively.

While much work has performed full state attitude inversion on simulated light curve data \cite{burton2024journal, gagnon2024, robinson2025att}, studies using real data often focus on determining a constant spin rate and axis of rotation for the observed object.

Frequency analysis in the form of periodograms, Fourier transforms, or epoch folding, is often used to determine the spin rate based on the light curve's frequency spectrum \cite{silha2015, silha2021, isoletta2024, schildknecht2015, pittet2017, yanagisawa2012, koshkin2018}. If optical material properties are known, the width of a single specular glint can provide sufficient information to determine the rotation rate \cite{hinks2016}. There has also been interest in tracking the evolution of spin rates over time for different classes of objects in different orbital regimes \cite{koshkin2018, blacketer2022, karpov2016}. These spin rate determination methods are designed for single-axis rotations and can fail for tumbling objects.

@@

The simplifying assumptions of constant, single-axis rotation that are commonly made when working with real data enable elegant solutions, but break down when the observed object is in a complex spin profile. Methods for full attitude state solutions -- time-varying orientation and angular velocities -- have been developed \cite{clark2022, burton2024journal, gagnon2024, linares2014particle}, but are seldom applied to real data. Works that have been successful at estimating a full rigid body attitude state from real data include genetic algorithms \cite{piergentili2020, gallucci2020} and brute-force grid search \cite{shafer2017}. Any full-state estimation method must tackle the inherent computational complexity, lack of knowledge of material reflectivities, and the presence of measurement noise.

In this paper, we describe a global full-state attitude solver inspired by recent PSO work \cite{burton2024journal} but is easier to tune, can be fully parallelized, and is robust to significant measurement noise \cite{robinson2025att}. Further, our method differs from other global estimation methods in that we do not seek to find one optimal solution and instead search for a collection of high-quality local minima to directly study the many ambiguous solutions for a given light curve. Our approach was designed specifically for use with real data as we take time-varying measurement noise and uncertainties in the body moments of inertia into account explicitly.

@@

This work proceeds by describing the inversion method, discussing efficient methods for computing the time-varying probability density of the light curve. We present inversion results for a simulated rocket body light curve where the ground truth is known, followed by two cases -- a derelict satellite and rocket body -- using real light curve data collected by the Purdue Optical Ground Station. A deeper treatment of our method and additional simulated light curve results can be found in \cite{robinson2025att}.

@@

The state vector $\vctr{x}$ is defined to be the concatenation of the Modified Rodriguez Parameter (MRP) $\vctr{p} = [p_1, p_2, p_3]^T$, the principal body frame angular velocity $\vctr{\omega} = [\omega_1, \omega_2, \omega_3]$ in radians per second, and the ratios of the principal moments of inertia $J_y / J_x$ and $J_z / J_x$ where the constant inertia tensor in principal axes is $J = \mathrm{diag}\left([J_x, J_y, J_z]\right)$:

@@

Our inversion method is based on the global minimization of a maximum-likelihood loss function which computes the negative log-likelihood of the observed light curve $\vctr{S}$ being a sample from the normal distribution defined by the estimated light curve mean $\hat{\vctr{S}}$ and the standard deviation at each $k$th timestep $\sigma_k$:

@@

\subsection{Computing Local Minima} \label{sec:run_solver}

Our multi-start solution method begins by creating $n$ guesses scattered throughout the solution space -- possibly sampled from a prior distribution based on available knowledge. In the most basic case, the initial state guess is sampled for guess $i$ at iteration $k=0$:

@@

\noindent
In this work, $\vctr{p}_{i,0}(0)$ is uniformly randomly sampled from orientation space, $\vctr{\omega}_{i,0}(0)$ is uniformly randomly sampled from the ball in $\mathbb{R}^3$ of radius $\norm{\vctr{\omega}}_\text{max}$ -- the maximum angular rate at which to initialize guesses -- while $\left(J_y / J_x\right)_{i,0}$ and $\left(J_z / J_x\right)_{i,0}$ are sampled from Gaussian prior distributions centered at estimated values derived from the known geometry of the object. We determine $\norm{\vctr{\omega}}_\text{max}$ based on the maximum power positive frequency in the observed light curve $f^\star$ in Hertz and an arbitrary safety factor $f_\omega \geq 1$, selected as $f_\omega = 1.25$ for this work:

@@

Even for a well-chosen bound $\norm{\vctr{\omega}}_\text{max}$, there may still be numerous high-quality solutions at significantly lower or higher angular velocities that possess equal $f^\star$ values due to object shape symmetries or harmonics in spin and precession rates, respectively. As a result, it is usually unwise to directly constrain the angular velocity to a given magnitude unless additional, unambiguous information is available.

@@

 In any particular illumination and observation condition, a fraction of the facet's area $\tilde{a}_i$ may be Sun- or observer-shadowed due to obstructing geometry before or after light reaches the surface element, respectively. The remainder of the facet's area $\bar{a}_i$ is unshadowed and contributes to the total flux reaching the observer from the object, such that the total area of each facet is $a_i = \tilde{a}_i + \bar{a}_i$. The geometry for an individual facet is displayed in Figure \ref{fig:facet_geom}.

@@

The unshadowed area $\bar{a}$ may be computed in several ways. For convex objects, $\bar{a}=a$ as self-shadowing is impossible. For highly nonconvex and detailed models composed of thousands of faces, $\bar{a}$ can be approximated on a pixel grid using shadow mapping \cite{robinson2022}. Self-shadowing can be efficiently solved semi-analytically for lower-fidelity approximations of real space object geometry by computing the mutual intersections of the polygons $P_k$ of other faces whose projections overlap with the face in question. Up to a maximum intersection depth $d$, selected for computation time, the unshadowed area can be computed via:

@@

As the objects we investigate in this work are well-approximated with relatively simple non-convex meshes, we use the semi-analytic method to efficiently compute unshadowed areas via the Sutherland-Hodgeman algorithm \cite{sutherland1974} for each polygon intersection. Further explanation of the polygon clipping procedure for computing the total shadowed area and accelerating this computation during inversion with the so-called shadow cache is included here \textbf{TODO: should this be a here? wording this felt weird if we're avoiding saying like "the authors'"} \cite{robinson2025att}.

@@

This section summarizes an in-depth study of relevant noise sources in CCD and CMOS sensor light curves which can be found in \cite{robinson2025twin}.

@@

\begin{table}[H]
  \centering
  \caption{Reflection properties of materials used in the synthetic data test case. The white paint parameters were estimated qualitatively}
  \vspace*{6pt}
  \begin{tabular}{|l|l|l|l|}
  \hline
  \textbf{Material} & $C_d$ & $C_s$ & $n$ \\ \hline
 Aluminum \cite{fankhauser2023} & $0.34$ & $0.40$ & $8.9$ \\ \hline
 White paint & $0.9$ & $0.1$ & $1$ \\ \hline
  \end{tabular}
  \label{tb:synth_matprops}
\end{table}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\figmed]{light_curves_mag_rocket_body_sdc.png}
  \caption{Simulated mean and sampled observations for the rocket body in V-band magnitude, with the variance included in blue.}
  \label{fig:obs_mag_synth}
\end{figure}

@@

A total of $10^5$ initial state guesses are created via the sampling scheme described in Section \ref{sec:run_solver} with $\norm{\vctr{\omega}}_\text{max}=5.26$ degrees per second. The inertia tensor ratios are initialized by sampling a symmetric Gaussian distribution with $\sigma=0.05 \: [kg\cdot m^2]$ on each axis to simulate a moderate level of inertia uncertainty. BFGS minimization is then performed for each initial guess to locally solve the optimization problem given by Equation \ref{eq:opt_problem}. Classifying candidate solutions with $\ell = 1/10$ produces over $10^4$ solutions within this bound. Figure \ref{fig:conv_lcs_synth} shows the mean light curves produced by the identified candidate solutions. There is good agreement between the candidate light curves and the observations, indicating that high-quality local minima have been identified.

@@

Figures \ref{fig:sigma_sols1} and \ref{fig:omega_sols1} display the candidate MRP and angular velocity vectors of the best solutions determined via the procedure in Section \ref{sec:candidate_sols}. We notice that for both the initial orientation in Figure \ref{fig:sigma_sols1} and angular velocity in Figure \ref{fig:omega_sols1}, the ground truth, plotted in red, lies squarely on a candidate solution surface. In angular velocity space, shown in Figure \ref{fig:omega_sols1}, most solutions fall onto the surface of two open-ended cylinders -- one with half the radius of the larger cylinder containing the truth. Similarly in orientation space, shown in Figure \ref{fig:sigma_sols1}, the solutions fall on two distinct manifolds -- likely resulting from a reflection of the object's body frame about the bisector between the Sun and observer vectors \cite{marto2024, burton2024journal}. One of these orientation-space surfaces contains the ground truth. These additional families of solutions highlight the reality that a wide variety of attitude profiles may produce nearly identical observations.

@@

This light curve shows clear periodicity, but has a high measurement standard deviation and a relatively low sampling rate due to the object's low brightness and the sensor readout time. Inversion was performed using $10^4$ initial guesses with the material and angular velocity assumptions listed in Table \ref{tb:case2_ass}. The candidate solution results are presented in terms of their mean light curves in Figure \ref{fig:case2_s}, orientation MRPs and angular velocities in Figure \ref{fig:case2_pw}, and inertia ratios in Figure \ref{fig:case2_i}.

@@

Attitude information is critical for many tasks informing space situational awareness. Orientation and angular velocity data aids high-fidelity orbit propagation, mission recovery efforts, and object selection for active debris removal. Obtaining attitude information is often difficult, especially for passive debris objects. Due to atmospheric distortion and diffraction-limited optics, ground-based telescopes can only determine a total brightness received from a space object. If a shape model is known, the light curve -- a sequence of these brightness measurements -- is one tool for attitude estimation. We presented an approach for solving this highly nonlinear and non-convex optimization problem with a gradient-based multi-start method. We presented attitude inversion results for one case with synthetic data and two cases with real observations. Unlike other approaches, our method successfully identifies the numerous ambiguous solutions families -- originating from symmetries in the observation geometry and the object shape -- which may produce the same observations. These disparate candidate solutions can serve as starting points for more detailed exploration as additional light curves or further object shape information is obtained.
